---
title: "LMS_Recap4R Exercise 2"
author: "MRC LMS"
date: "`r format(Sys.time(), '%B %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

These exercises cover the sections of Recap in R [LMS_Recap4R](https://lmsbioinformatics.github.io/LMS_PlottingInR/course/R_Recap_n_RegularExp_Presentation.html#).


```{r,echo=F,eval=F}
setwd("/Users/yfwang/GitHub_project/LMS_Recap4R/course/exercise/")
```

```{r,echo=F,eval=T}
episodeExercise_df <- read.csv("../GoT_dataset/episode_data.csv")
```

# Exercise 2

* use _grep()_ function and _grepl()_ function to help us understand how `regular expressions` work in R. 

Please load dataset `"GoT_dataset/episode_data.csv"` as **data.frame** and name it as `episodeExercise_df.` Then add a new column `Contain.Winter` to `episodeExercise_df`. If the `episode_name` column contains "Winter", `Contain.Winter` == "TRUE", otherwise `Contain.Winter` == "FALSE". Please subset this **data.frame** and keep rows with "Winter" in the episodeExercise_df.$episode_name.


* we use _sub()_ function again to help us understand how `regular expressions` work in R. In episodeExercise_df_winter1$episode_name, if **Winter** is straight after " at the beginning of the string, replace it with **Spring**. If **Winter** is at the end of the string just before ", replace it with **Summer**. Keep **Winterfell** unchanged.



